6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex

Certainly one thing we definitely plan on doing if we end up trying to turn this project into a publishable paper is to include all of the articles in our dataset. With the much greater sample size and the much more expansive corpus from the additional articles, we might expect to see drastically different 
%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering

>>>>

Another way we could improve our model is to apply a basis expansion to our variables to include polynomial and various interaction terms. In many cases, theres no good justification to why a feature is linearly related to the output feature. Hence, applying a polynomial expansion might uncover an entirely different relationship between our dependent variable and its covariates. We also think that interaction terms might provide some significant predictive power.

Certainly one thing we definitely plan on doing if we end up trying to turn this project into a publishable paper is to include all of the articles in our dataset. With the much greater sample size and the much more expansive corpus from the additional articles, we might expect to see drastically different optimal weights. 
%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering
